\bf Faster Neural Machine Translation Inference

### 2018-01-26 fast-beam/fast-beam.tex
fast beam paper

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \STATE $sum \gets sum + e^{p_i}$
\ENDFOR

@@

\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets \frac{e^{p_i}}{sum} $
\ENDFOR

@@

\COMMENT{calculate softmax($p_i$)}
\RETURN $\frac{e^{max}}{sum}$, $argmax$

\end{algorithmic}
\caption{Fused Kernel}
\label{algo:Fused Kernel}
\end{figure}

@@

For inference, we used and extend Amun (???), the fastest open-source inference engine we are aware of for RNN/GRU model used in this paper. Mini-batch was set to 128 sentences, unless explicitly stated, and a maxi-batch was ten times that of mini-batch.

All experiments was performed on an Nvidia GTX 1060 GPU. The host contains 8 Intel hypercores running at 2.8Ghz, 16GB RAM and SSD hard drive.

>>>>

\STATE $sum \gets 0$ 
\FORALL{$p_i$ in $p$}
  \STATE $sum \gets sum + e^{p_i - max}$
\ENDFOR

@@

\FORALL{$p_i$ in $p$}
  \STATE $p_i \gets \frac{e^{p_i} - max}{sum} $
\ENDFOR

@@

\COMMENT{calculate softmax($p_i$)}
\RETURN $\frac{1}{sum}$, $argmax$

\end{algorithmic}
\caption{Combined softmax and argmax}
\label{algo:Fused Kernel}
\end{figure}

@@

For inference, we used and extend Amun (???), the fastest open-source inference engine we are aware of for the model used in this paper. We uused a mini-batch of 128 sentences and maxi-batch of 1280 sentences, unless otherwise stated.

The hardware used in all experiments was an Nvidia GTX 1060 GPU on a host containing 8 Intel hypercores running at 2.8Ghz, 16GB RAM and SSD hard drive.
